\input{header.tex}

\title{Introduction}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\section{Object-oriented programming}

\begin{frame}{Pradigma}
OOP is a programming pradigma

Objects contain
\begin{itemize}
\item data (ak. attribute)
\item code (ak. methods)
\end{itemize}

\end{frame}

\begin{frame}{OOP vs. Procedural}

\begin{block}{Procedural}
data tends to be highly decoupled from the functions that operate on it
\end{block}

\begin{block}{Object-oriented}
data tends to carry with it a collection of functions
\end{block}

\note{http://stackoverflow.com/a/552474/6632389}

\end{frame}

\section{Object-oriented concepts}

\begin{frame}{Classes and objects}

\begin{block}{Class}
The blueprint for an object. Defines how a object should be created.
\end{block}

\begin{block}{Object}
An instance of a class. Gets created during runtime.
\end{block}

\end{frame}

\begin{frame}{Information hidding}
Encapsulate data and hide the internal structure from caller. This allows
changing the internal details without affecting 
\end{frame}

\begin{frame}{Inheritance}
Exentend or overwrite functionality of another class.
\end{frame}

\begin{frame}{Interface}
Define a method without implementing it as an interface to be used by other
classes.
\end{frame}

\begin{frame}{Polymorphism}
\framesubtitle{aka Subtyping}
Define a implementation for a specialied type.
\end{frame}

\section{C++}
\subsection{Overview}
\begin{frame}{C++ - Overview}
\begin{itemize}
  \item compiled language
  \item general-purpose programming language
  \item Multi-pradigma
  \begin{itemize}
    \item procedural
    \item functional
    \item object-oriented
    \item generic
  \end{itemize}
  \item statically typed
  \item allows low-level memory manipulation
  \item designed for large, resource constrained systems 
\end{itemize}
\end{frame}

\subsection{Standardization}
\begin{frame}{C++ - Standardization}
\itemize{}
\item[1979] C with Classes first implemented 
\item[1998] C++98 (ISO/IEC 14882:1998) 
\item[2003] C++03 (ISO/IEC 14882:2003)
\item[2011] C++11 (ISO/IEC 14882:2011)
\note[item]{C++11 major extension over C++03} 
\item[2014] C++14 (ISO/IEC 14882:2014)
\note[item]{C++14 small extension over C++11, featuring mainly bug fixes
 and small improvements}
\item[2017] C++17 (also called C++1z)
\end{frame}

\begin{frame}{Emedded Systems}
\begin{itemize}
  \item Embedded C++ (still in use?)
\end{itemize}
\end{frame}

\end{document}
